Eliminating object prior-bias from sparse-projection tomographic reconstructions

### 2021-09-19 paper/changes.tex
Finetuned our response to reviewers

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx}
\bibliographystyle{IEEEtran}
\usepackage{caption}
\usepackage{subcaption}

\usepackage{boxedminipage}
\usepackage{a4wide}
\usepackage{subcaption}
\usepackage[colorlinks=true]{hyperref}
\title{Response to Reviewers and Associate Editor}
\begin{document}
\date{}
\maketitle

This paper was submitted earlier, and out of the three reviewers, two of them had pronounced this as ``publish unaltered'' and one reviewer (R1) did not recommend resubmission.

The handling Editor has encouraged a resubmission of this paper taking into account the comments of R1.  In particular, R1 has these concerns and we quote these
\begin{quote}
  The authors have spent considerable effort in revising the
  manuscript and addressing the concerns of the reviewers. I would
  like to thank the authors for their effort. I believe the manuscript
  has improved because of these revisions, especially in the structure
  of the paper and the discussion of related work. Unfortunately, some
  of my main concerns with regards to the experiments, the accuracy of
  the proposed method, and the presentation of the findings remain
  present in the revised manuscript. In some cases the revisions have
  even increased my concerns about certain aspects. Mainly, the
  included experiments still do not clearly show that the proposed
  method improves upon existing ‘simple’ prior-based methods, and the
  new results even show that there is evidence that FDK is more
  accurate than the proposed method exactly in the region that changed
  \end{quote}

In this document, we explain the steps we have taken to address the
reviews received in our previous submission to TCI. In particular,
we address the main concern of the reviewer below.

\begin{itemize}
\item \textbf{Simple methods are better, why yours?}

@@

  That said, the goal of our previous and curent work is to provide a
  technique that can improve upon a chosen baseline reconstruction
  when measurements are extremely sparse. One may choose any baseline
  reconstruction for pedagogical, historical, or commercial reasons,
  and is there a way to improve?

@@

  As far as FDK is concerned, the current results indeed show the
  superiority of the TV-based scheme (as also noted by the reviewer).

\item \textbf{Other comments given by Reviewer R1 and the handling editor}

 \begin{itemize}
  \item \textbf{Machine Learning}

@@

  %% thousands of time instants at which the previous voxel intensities
  %% are known for each voxel. This amount of data is not available to
  %% us, and may be hard to acquire because each specimen is usually
  %% scanned only a couple of times in any longitudinal study.

  Further, a specific `event-of-interest' may occur just once in a
  longitudinal study and hence training on data of all previous time
  instants may be misleading. If however, we use measurements from
  identical and full-cycle longitudinal studies (including
  events-of-interest) of similar specimen (instead of the `same'
  specimen as we used), a deep-learning technique may be applied. We
  see this as an extension of using object-prior generated from the
  same object, and hence we have not explored this direction.

@@

\item \textbf{Details of other methods used for comparison}
 We have compared our method with Algebraic Reconstruction Technique
 (ART), Simultaneous Algebraic Reconstruction Technique (SART),
 Simultaneous Iterative Reconstruction Technique (SIRT), Total
 Variation (TV) and Compressed Sensing (CS) with Haar wavelet and DCT
 as sparsity basis. The details of solvers used for these
 algorithms are now mentioned in Page.~7 (Section-6A). For CS
 reconstruction, we observed that Haar wavelet and DCT were best
 suited for our dataset among various other possible sparsity basis.

\item \textbf{Discussion about Metrics used}
  In our experiments, we observed that for a given dataset and a set of projection measurements, the intensity span of histograms of reconstructed volumes differ across various methods and solvers. Hence, we choose to focus on preserving the structures on our reconstructions, and not rely on the absolute intensity values alone. Hence, we choose SSIM with a higher weightage to structure-preservation. For our record, we have computed RMSE values as well and they are presented here in Tables~\ref{table:potato_rmse} and~\ref{table:sprouts_rmse}.

@@

\item \textbf{Dicsussion about Computational Cost}\\
  We now present details of both time and space complexities of our technique in Section.7B of our paper.
\end{itemize}

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx}
\bibliographystyle{IEEEtran}
\usepackage{caption}
\usepackage{subcaption, tabularx}
\usepackage{xcolor}
\usepackage{boxedminipage}
\usepackage{a4wide}
\usepackage{subcaption}
\usepackage[colorlinks=true]{hyperref}
\title{Response to Reviewers and Associate Editor}
\begin{document}
\date{}
\maketitle

This paper was submitted earlier, and out of the three reviewers, two of them had pronounced this as ``publish unaltered'' and one reviewer (R1) did not recommend resubmission. The handling Editor has encouraged a resubmission of this paper taking into account the comments of R1.  We thank all reviewers for their remarks and in this document, we explain the steps we have taken to address the reviews received in our previous submission to TCI. R1 has these concerns and we quote these
\begin{quote}
  \textcolor{blue}{The authors have spent considerable effort in revising the
  manuscript and addressing the concerns of the reviewers. I would
  like to thank the authors for their effort. I believe the manuscript
  has improved because of these revisions, especially in the structure
  of the paper and the discussion of related work. Unfortunately, some
  of my main concerns with regards to the experiments, the accuracy of
  the proposed method, and the presentation of the findings remain
  present in the revised manuscript. In some cases the revisions have
  even increased my concerns about certain aspects. Mainly, the
  included experiments still do not clearly show that the proposed
  method improves upon existing ‘simple’ prior-based methods, and the
  new results even show that there is evidence that FDK is more
  accurate than the proposed method exactly in the region that changed}
  \end{quote}

\begin{itemize}
\item \textbf{In particular, we address the following main concern of the reviewer below.}\\

    \textcolor{blue}{Note that the total
variation minimization results are much better than the l1-ls results that the authors show in the
paper.}\\

@@

  That said, the goal of our previous and curent work is to provide a
  technique that can improve upon a chosen baseline reconstruction
  when measurements are extremely sparse.  One may choose any baseline
  reconstruction for pedagogical, historical, or commercial reasons,
  and given that, our key question is-- is there a way to improve?

@@

  As far as FDK is concerned, the current results indeed show the
  superiority of the TV-based scheme (as also noted by the reviewer).
  \clearpage
\item \textbf{Other comments given by Reviewer R1 and the handling editor}

 \begin{itemize}
 \item    \textcolor{blue}{...the paper should at least include a (short) discussion about the
     possibility of using deep learning for this, and its disadvantages.}

   We have now discussed the difficulties in using deep-learning
   techniques for the current problem in Sec.~7C of our paper. We also
   describe them here below.

@@

  %% thousands of time instants at which the previous voxel
  %% intensities are known for each voxel. This amount of data is not
  %% available to us, and may be hard to acquire because each specimen
  %% is usually scanned only a couple of times in any longitudinal
  %% study.

  Further, a specific `event-of-interest' may occur just once in a
  longitudinal study and hence training on data of all previous time
  instants may be misleading. If however, we use measurements from
  identical and full-cycle longitudinal studies, including
  events-of-interest, of similar specimen (instead of the `same'
  specimen as we used), a deep-learning technique may be applied. We
  see this as an extension of using object-prior generated from the
  same object, and hence we have not explored this direction.

@@

\item \textcolor{blue}{There are no added comparisons with popular existing methods for
  reconstruction with a small number of projections (TV, algebraic techniques, etcetera)}\\

 Among the family of algebraic techniques, we have compared our method
 with Algebraic Reconstruction Technique (ART) and Simultaneous
 Algebraic Reconstruction Technique (SART). We do not reconstruct
 using Discrete Algebraic Reconstruction Technique (DART) since there
 is no prior information about the number of possible attentuation
 coefficients in the test object. Among other iterative techniques, we
 have used Simultaneous Iterative Reconstruction Technique (SIRT),
 Total Variation (TV) and Compressed Sensing (CS) with Haar wavelet
 and DCT as sparsity basis. The details of solvers used for these
 algorithms and their reconstructions are in Page.~7 (Section-6A) of
 the paper. For CS reconstruction, we observed that Haar wavelet and
 DCT were best suited for our dataset among various other possible
 sparsity basis.

\item \textcolor{blue}{Why did the authors not choose the standard
  settings for SSIM?...I don’t understand the reason given for not
  including RMSE: the values don’t have to be optimized again -- you
  could just optimize for SSIM but at least still report RMSE
  comparisons.}\\

  In our experiments, we observed that for a given dataset and a set of projection measurements, the intensity span of histograms of reconstructed volumes differ across various methods and solvers. Hence, we choose to focus on preserving the structures on our reconstructions, and not rely on the absolute intensity values alone. Hence, we choose SSIM with a higher weightage to structure-preservation. For our record, we have computed RMSE values as well and they are presented here in Tables~\ref{table:potato_rmse} and~\ref{table:sprouts_rmse}.

@@

\item  \textcolor{blue}{A discussion about computational costs (time, memory) should be included in the paper.}

  We now present details of both time and space complexities of our technique in Section.7B of our paper.

Most of the
computation time in our technique is used for the generation of low quality eigen-space
by reconstructing each of the templates using TV and FDK. If the set of projection views for every test is fixed a priori, the set of low quality reconstructions can be produced offline and stored in order to save computational costs. With this assumption, Table~\ref{table:compute_time} shows the computation times for various stages of reconstruction of a 2D slice of Liver on MATLAB 2019a on an  AMD 2920X 12-Core Processor machine with 64GB RAM. If however, new sets of projection views for every test are to be allowed, the low quality reconstructions can still be performed efficiently using parallelization since these reconstructions are completely independent. Here below, we describe the
time complexity of spatially-varying prior technique.  If
\begin{itemize}
\item $N =$ number of voxels of the volume
\item $T =$ number of templates available, and
\item $F =$ time taken for iterative TV optimization,
\end{itemize}
then, the computational complexity is sum of the following
\begin{itemize}
\item $O(NT^2+T^3)$ for creating the eigenspace,
\item $O(NT^2)$ for deriving the weights map, and
\item time $F$  taken for iterative minimization
\end{itemize}
where $O(.)$ is the notation for `Big O' used in complexity analysis. 
In terms of space, the complexity is $O(T)$ in order to store the templates and their low quality reconstructions. We only need to store a single weights map volume regardless of the number of templates available.

\begin{table}[]
  \centering
  \caption{Computation times (in seconds) for various stages of reconstruction of a 2D slice of Liver on MATLAB 2019a on an  AMD 2920X 12-Core Processor machine with 64GB RAM. Here we assume that low quality eigen-spaces of the templates are computed offline.}
\begin{tabular}{|l|l|l|l|}
\hline
Backprojection             & TV                        & \begin{tabular}[c]{@{}l@{}}Computation of \\ weights map\end{tabular} & \begin{tabular}[c]{@{}l@{}}Final reconstruction\\ with spatially-varying \\ prior\end{tabular} \\ \hline
\multicolumn{1}{|c|}{0.40} & \multicolumn{1}{c|}{8.44} & \multicolumn{1}{c|}{0.04}                                             & \multicolumn{1}{c|}{46.73}                                                                     \\ \hline
\end{tabular}
\label{table:compute_time}
\end{table}
\end{itemize}

### 2021-09-19 paper/post_tci.tex
Finetuned our response to reviewers

In this section, we first illustrate the advantage of using multiple types of eigenspaces for the computation of weights map, and then present reconstruction results on all datasets. For quantitative evaluation, we compute the Structural Similarity Index Metric\footnote{Here, we assign higher importance to the preservation of structure in a reconstruction by assigning the following weights to (structure, contrast, intensity): $(0.7,0.2,0.1)$.} (SSIM)~\cite{ssim}.

@@

The test volume was reconstructed from a partial set of 18 real
cone-beam projections, i.e., $2\%$ of the $900$ projection views from
which ground truth was reconstructed (see remarks in
Sec.~\ref{sec:potatoAndOkra}). 2D reconstructions of one of the slices
is shown in Fig.~\ref{fig:potato_2D_results}. A complete 3D
reconstruction can be found in the supplementary
material~\cite{supp_paper}. The red RoI spans 7 consecutive slices
where the test is different from all of the previously scanned
objects. %The zoomed-in images around the major region of change (red
%RoI) is shown in Fig.~\ref{fig:potato_zoomed_2D_results}. 
\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\fcolorbox{blue}{blue}{\includegraphics[width=0.22\columnwidth]{../images/potato/post_tci/testIm_paper.png}}}
\subcaptionbox{FDK, no prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/fbp.png}}
\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/tv_lambdaTV_0.05.png}}
\subcaptionbox{This paper}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/weighted_prior_kk_30_lambda_prior_1.100000.png}}
\caption{Reconstruction of potato from 6 projection views--(b) has strong streak artefacts with unclear structure of the potato, (c) largely blurred, and (c) is sharper with significantly reduced streak artefacts. 3D reconstructions from 18 cone-beam views can be seen in the supplementary material~\cite{supp_paper}. }
\label{fig:potato_2D_results}
\end{figure}

@@

%--------------------------Okra-- results
\subsubsection{\textbf{Okra}}
\label{Sec:okra_spatially_varying}
The test volume was reconstructed from a partial set of 30 real
cone-beam projections, i.e., $6.7\%$ of the $450$ projection views from which
ground truth was reconstructed (refer Sec.~\ref{sec:datasets}). 2D reconstructions of one of the
slices is shown in Fig.~\ref{fig:okra_2D_results}. A complete 3D
reconstruction can be found in in the supplementary material
~\cite{supp_paper}. The red RoI spans 7 consecutive slices where the
test is different from all of the previously scanned objects. %A
%zoomed-in region around the major region of change (red RoI) is shown
%in Fig.~\ref{fig:okra_zoomed_2D_results}.
As in the test, the
reconstruction by spatially-varying method shows the absence of the
deformity and better removal of sub-sampling artefacts when compared
to FDK and TV. This is also seen in the SSIM values in
Table~\ref{table:okra_ssim}.

\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\fcolorbox{cyan}{cyan}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/input_roi.png}}}
\subcaptionbox{FBP, no prior}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/FBP_cropped.png}}
\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/TV_cropped.png}}
%\subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
\subcaptionbox{This paper}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/weighted_prior_cropped.png}}
\caption{Reconstruction of okra from 48 projection views
   (b) has streaky artefacts, (c) has blurred structures and (d) is sharper with significantly less streaky artefacts. 3D reconstructions from 30 cone-beam views can be seen in the supplementary material~\cite{supp_paper}.}
\label{fig:okra_2D_results}
\end{figure}

@@

%--------------------RFA 2 few views
\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\fcolorbox{white}{green}{\includegraphics[width=0.23\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/colorTestIm.png}}}\hfill
\subcaptionbox{Backprojection\\no prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/fbp.png}}\hfill
\subcaptionbox{TV, no prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/tv_lambdaTV_0.036.png}}\hfill
\subcaptionbox{This paper}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/weighted_prior_kk_30_lambda_prior_1.100000.png}}
\caption{\small{ Reconstruction of `test' (slice 7) from Fig.~\ref{fig:RFA2_test_object-prior} from only 30 views, using (b) FBP and no prior resulting in streaks (c) TV resulting in blurred bone structures and (d) spatially varying object-prior (slices 1-6 of Fig.~\ref{fig:RFA2_test_object-prior} are used as object-prior) resulting in clear bone structures with less streaks. The region enclosed in red rectangle is our Region of Interest (RoI) as it contains both the new position of the needle and some background.}}
\label{fig:tmh_2D_results}
\end{figure}

@@

The test volume was reconstructed from partial set of 30 
cone-beam projections, i.e., $1.7\%$ of the $1800$ projection views
from which ground truth was reconstructed (refer
Sec.~\ref{sec:datasets}). The selected 3D ground truth of template
volumes, test volume, as well as the 3D reconstructions are shown in
the supplementary material~\cite{supp_paper}. For the sake of
exposition, the red region of interest (RoI) has been culled out from
7 consecutive slices in the 3D volume to indicate new structures;
other changes can be viewed in the video.  2D reconstruction of one of
the slices is shown in Fig.~\ref{fig:sprouts_2D_results}.
Table~\ref{table:sprouts_ssim} shows the improvement in SSIM of the
reconstructed new regions as compared to other methods.
%----------------------------------------------------

\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\fcolorbox{yellow}{yellow}{\includegraphics[width=0.22\columnwidth]{../images/sprouts/post_TCI/2D/20_views/testIm_roi.png}}}
\subcaptionbox{FDK, no prior}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/fbp.png}}
\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/tv_lambdaTV_0.100.png}}
\subcaptionbox{This paper}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/weighted_prior_kk_30_lambda_prior_2.100000.png}}
\caption{Reconstruction of sprouts from 20 projection views
   (b) has streaky artefacts, (c) has blurred structures and (d) is sharper with significantly less streaky artefacts. 3D reconstructions from 30 cone-beam views can be seen in the supplementary material~\cite{supp_paper}.}
\label{fig:sprouts_2D_results}
\end{figure}

@@

\section{Discussion}
\label{sec:discussion}
In this section, we discuss tuning of parameters and the computational complexity of our method.
\subsection{Tuning of parameters:}
$\lambda_1$, $\lambda_2$ and $k$ are the three
hyper-parameters that need to be chosen carefully for optimal
reconstruction. In our experiments, $\lambda_1$ was tuned to maximize
SSIM of the whole reconstructed test volume for TV reconstruction of
each dataset. This value was retained for spatially-varying
prior-based reconstruction as well. The value of $\lambda_2$ largely
depends on the amount of artefacts we aim to remove by using
object-prior at the cost of their dominance in the new regions. This
value was chosen to lie between $0-3$ for our datasets. Finally, the
hyper-parameter $k$ defines the sensitivity of the weights map to the
difference between test image and object-prior (projection of
test onto the space of object-prior). When $k=0$, our method 
behaves similar to the reconstruction using TV-only regularization. As $k$ increases, the weights map starts
capturing new changes in the test, at the cost of detecting a few
false positives i.e., false new changes. In other words, as the
weights-map becomes more sensitive to the difference between the test
and object-prior, it becomes more noisy. In order to visualize the
effect of the hyper-parameter $k$, we performed 2D reconstructions on
okra dataset for different values of
$k$. Fig.~\ref{fig:few_view_okra_2D_weights} shows the weights map
obtained for each of the $k$ values and
Fig.~\ref{fig:reconstructions_as_k_varies} shows the corresponding
final reconstructions. We run our experiments for a few values of $k$
and choose the best reconstruction based on our tolerance for noise
in the weights-map.
When a large number of templates are available, this parameter can be
chosen by assuming one of the templates as test and choosing the $k$
that gave the best reconstruction. Alternatively, in cases where one
wishes to completely avoid the use of this hyper-parameter, one can
construct a binary weights-map using a learning based method described
in the supplementary material~\cite{supp_paper}.

@@

The use of object-priors does introduce additional time and space complexities when compared to the use of a simpler prior such as TV-only prior.  For spatially-varying prior, most of the
computation time is used in the generation of low quality eigen-space
by reconstructing each of the templates using TV and FDK. If the set of projection views for every test is fixed a priori, the set of low quality reconstructions can be produced offline and stored, in order to save computational costs. If however, new sets of projection views for every test are to be allowed, the low quality reconstructions can still be performed efficiently using parallelization since these reconstructions are completely independent. Here below, we describe the

@@

where $O(.)$ is the notation for `Big O' used in complexity analysis. In terms of space, the complexity is $O(T)$ in order to store the templates and their low quality reconstructions. We need to store a single weights map volume regardless of the number of templates available.

>>>>

In this section, we first illustrate the advantage of using multiple types of eigenspaces for the computation of weights map, and then present reconstruction results on all datasets. For quantitative evaluation, we compute the Structural Similarity Index Metric (SSIM)~\cite{ssim}. Here, we assign higher importance to the preservation of structure in a reconstruction by assigning the following weights to structure, contrast and intensity respectively: $0.7,0.2,0.1$.

@@

The test volume was reconstructed from a partial set of $2\%$ of projection views from
which ground truth was reconstructed (see remarks in
Sec.~\ref{sec:potatoAndOkra}). 2D reconstructions of one of the slices
is shown in Fig.~\ref{fig:potato_2D_results}. A complete 3D
reconstruction can be found in the supplementary
material~\cite{supp_paper}. The red RoI spans 7 consecutive slices
where the test is different from all of the previously scanned
objects. %The zoomed-in images around the major region of change (red
%RoI) is shown in Fig.~\ref{fig:potato_zoomed_2D_results}. 
\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\fcolorbox{blue}{blue}{\includegraphics[width=0.22\columnwidth]{../images/potato/post_tci/testIm_paper.png}}}
\subcaptionbox{FBP, no prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/fbp.png}}
\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/tv_lambdaTV_0.05.png}}
\subcaptionbox{This paper}{\includegraphics[width=0.23\columnwidth]{../images/potato/post_tci/6_views/weighted_prior_kk_30_lambda_prior_1.100000.png}}
\caption{Reconstruction of potato from 6 projection views--(b) has strong streak artefacts with unclear structure of the potato, (c) largely blurred, and (c) is sharper with significantly reduced streak artefacts.}
\label{fig:potato_2D_results}
\end{figure}

@@

%--------------------------Okra-- results
\subsubsection{\textbf{Okra}}
\label{Sec:okra_spatially_varying}
The test volume was reconstructed from a partial set of $6.7\%$ of projection views from which
ground truth was reconstructed (refer Sec.~\ref{sec:datasets}). 2D reconstructions of one of the
slices is shown in Fig.~\ref{fig:okra_2D_results}. A complete 3D
reconstruction can be found in in the supplementary material
~\cite{supp_paper}. The red RoI spans 7 consecutive slices where the
test is different from all of the previously scanned objects. %A
%zoomed-in region around the major region of change (red RoI) is shown
%in Fig.~\ref{fig:okra_zoomed_2D_results}.
As in the test, the
reconstruction by spatially-varying method shows the absence of the
deformity and better removal of sub-sampling artefacts when compared
to FDK and TV. This is also seen in the SSIM values in
Table~\ref{table:okra_ssim}.

\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\fcolorbox{cyan}{cyan}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/input_roi.png}}}
\subcaptionbox{FBP, no prior}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/FBP_cropped.png}}
\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/TV_cropped.png}}
%\subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
\subcaptionbox{This paper}{\includegraphics[width=0.23\columnwidth]{../images/okra/post_TCI/2D/48_views/weighted_prior_cropped.png}}
\caption{Reconstruction of okra from 48 projection views
   (b) has streaky artefacts, (c) has blurred structures and (d) is sharper with significantly less streaky artefacts.}
\label{fig:okra_2D_results}
\end{figure}

@@

%--------------------RFA 2 few views
\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\fcolorbox{white}{green}{\includegraphics[width=0.23\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/colorTestIm.png}}}\hfill
\subcaptionbox{FBP, no prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/fbp.png}}\hfill
\subcaptionbox{TV, no prior}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/tv_lambdaTV_0.036.png}}\hfill
\subcaptionbox{This paper}{\includegraphics[width=0.24\columnwidth]{../images/tmh/RFA2/post_TCI/very_few_views/weighted_prior_kk_30_lambda_prior_1.100000.png}}
\caption{\small{ Reconstruction of `test' (slice 7) from Fig.~\ref{fig:RFA2_test_object-prior} from only 30 views, using (b) FBP and no prior resulting in streaks (c) TV resulting in blurred bone structures and (d) spatially varying object-prior (slices 1-6 of Fig.~\ref{fig:RFA2_test_object-prior} are used as object-prior) resulting in clear bone structures with less streaks. The region enclosed in red rectangle is our Region of Interest (RoI) as it contains both the new position of the needle and some background.}}
\label{fig:tmh_2D_results}
\end{figure}

@@

The test volume was reconstructed from a partial set of  
 $1.7\%$ of projection views
from which ground truth was reconstructed (refer
Sec.~\ref{sec:datasets}). The selected 3D ground truth of template
volumes, test volume, as well as the 3D reconstructions are shown in
the supplementary material~\cite{supp_paper}. For the sake of
exposition, the red region of interest (RoI) has been culled out from
7 consecutive slices in the 3D volume to indicate new structures;
other changes can be viewed in the video.  2D reconstruction of one of
the slices is shown in Fig.~\ref{fig:sprouts_2D_results}.
Table~\ref{table:sprouts_ssim} shows the improvement in SSIM of the
reconstructed new regions as compared to other methods.
%----------------------------------------------------

\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\fcolorbox{yellow}{yellow}{\includegraphics[width=0.22\columnwidth]{../images/sprouts/post_TCI/2D/20_views/testIm_roi.png}}}
\subcaptionbox{FBP, no prior}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/fbp.png}}
\subcaptionbox{TV, no prior}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/tv_lambdaTV_0.100.png}}
\subcaptionbox{This paper}{\includegraphics[width=0.23\columnwidth]{../images/sprouts/post_TCI/2D/20_views/weighted_prior_kk_30_lambda_prior_2.100000.png}}
\caption{Reconstruction of sprouts from 20 projection views
   (b) has streaky artefacts, (c) has blurred structures and (d) is sharper with significantly less streaky artefacts.}
\label{fig:sprouts_2D_results}
\end{figure}

@@

\section{Discussion}
\label{sec:discussion}
In this section, we discuss tuning of parameters, computational complexity of our method, and requirements for applying deep learning techniques in longitudinal few-view reconstruction.
\subsection{Tuning of parameters:}
$\lambda_1$, $\lambda_2$ and $k$ are the three
hyper-parameters that need to be chosen carefully for optimal
reconstruction. In our experiments, $\lambda_1$ was tuned to maximize
SSIM of the whole reconstructed test volume for TV reconstruction of
each dataset. This value was retained for spatially-varying
prior-based reconstruction as well. The value of $\lambda_2$ largely
depends on the amount of artefacts we aim to remove by using
object-prior at the cost of their dominance in the new regions. This
value was chosen to lie between $0-3$ for our datasets. Finally, the
hyper-parameter $k$ defines the sensitivity of the weights map to the
difference between test image and object-prior (projection of
test onto the space of object-prior). When $k=0$, our method 
behaves similar to the reconstruction using TV-only regularization. As $k$ increases, the weights map starts
capturing new changes in the test, at the cost of detecting a few
false positives i.e., false new changes. In other words, as the
weights-map becomes more sensitive to the difference between the test
and object-prior, it becomes more noisy. In order to visualize the
effect of the hyper-parameter $k$, we performed 2D reconstructions on
okra dataset for different values of
$k$. Fig.~\ref{fig:few_view_okra_2D_weights} shows the weights map
obtained for each of the $k$ values and
Fig.~\ref{fig:reconstructions_as_k_varies} shows the corresponding
final reconstructions. We run our experiments for a few values of $k$
and choose the best reconstruction based on our tolerance for noise
in the weights-map.
When a large number of templates are available, this parameter can be
chosen by assuming one of the templates as test and choosing the $k$
that gave the best reconstruction. Alternatively, in cases where one
wishes to completely avoid the use of this hyper-parameter, one can
construct a binary weights-map using a learning based method described
in the supplementary material~\cite{supp_paper}.

@@

Most of the
computation time in our technique is used for the generation of low quality eigen-space
by reconstructing each of the templates using TV and FDK. If the set of projection views for every test is fixed a priori, the set of low quality reconstructions can be produced offline and stored in order to save computational costs. With this assumption, Table~\ref{table:compute_time} shows the computation times for various stages of reconstruction of a 2D slice of Liver on MATLAB 2019a on an  AMD 2920X 12-Core Processor machine with 64GB RAM. If however, new sets of projection views for every test are to be allowed, the low quality reconstructions can still be performed efficiently using parallelization since these reconstructions are completely independent. Here below, we describe the

@@

where $O(.)$ is the notation for `Big O' used in complexity analysis. 
In terms of space, the complexity is $O(T)$ in order to store the templates and their low quality reconstructions. We only need to store a single weights map volume regardless of the number of templates available.

\begin{table}[]
 \centering
  \caption{Computation times (in seconds) for various stages of reconstruction of a 2D slice of Liver on MATLAB 2019a on an  AMD 2920X 12-Core Processor machine with 64GB RAM. Here we assume that low quality eigen-spaces of the templates are computed offline.}
\begin{tabular}{|l|l|l|l|}
\hline
Backprojection             & TV                        & \begin{tabular}[c]{@{}l@{}}Computation of \\ weights map\end{tabular} & \begin{tabular}[c]{@{}l@{}}Final reconstruction\\ with spatially-varying \\ prior\end{tabular} \\ \hline
\multicolumn{1}{|c|}{0.40} & \multicolumn{1}{c|}{8.44} & \multicolumn{1}{c|}{0.04}                                             & \multicolumn{1}{c|}{46.73}                                                                     \\ \hline
\end{tabular}
\label{table:compute_time}
\end{table}
\subsection{Requirements for applying deep learning techniques}
Deep learning techniques are powerful tools to learn an unknown
parameteric function relating an input space and an output space. In such
settings, our current goal of detecting new changes is a `prediction'
problem in a continuous solution space i.e., \textit{``given
  intensities of a voxel at various time instants in a longitudinal
  setting and partial measurements of the voxel at the current time,
  what will be the intensity of the same voxel at the current time
  instant?''}. This estimation can be learnt by a deep neural network
if there are hundreds of labeled data.  However, generalization of
this across multiple datasets poses a question mark.

  Further, a specific `event-of-interest' may occur just once in a
  longitudinal study and hence training on data of all previous time
  instants may be misleading. If however, we use measurements from
  identical and full-cycle longitudinal studies, including
  events-of-interest, of similar specimen (instead of the `same'
  specimen as we used), a deep-learning technique may be applied. We
  see this as an extension of using object-prior generated from the
  same object.

  Another avenue for using deep networks \textit{within} our current
  work is to replace the currently used fixed eigenspace provided by
  PCA by a learnt feature basis provided by a network such as an
  autoencoder. For each dataset, an autoencoder may be trained to
  learn a specific set of latent features. This will again require
  atleast a few tens of volumes. We see this as a future direction of
  work.
